\documentclass[12pt]{article}
\usepackage[a4paper, top=1cm, bottom=2cm, left=2cm,right=2cm]{geometry}
\pagenumbering{gooble}
\parindent 0px
\usepackage{enumerate}
\title{Curriculum Vitae \par MD.MINHAJUL SHARIAR ZAMAN ALIF \par House no-08 \par Road no-20/A \par Sector-04,Uttara,Dhaka-1230 \par 01905058778$|$ 23-54144-3@student.aiub.edu}
\date{ }
\begin{document}
	\maketitle
	%--------------------ACADEMIC CREDENTIALS----------------
	\begin{large}
		\underline {\textbf{Academic Credentials}} 
	\end{large}
	
	\begin{itemize}
		\item \textbf{Secondary School Certificate} \hfill \textbf{2018-2020}
		\begin{itemize}
			\item Scholars' School \&\ College.
			
			\item Subject: Science.
			\item G.P.A: 4.06
		\end{itemize}
		\item \textbf{Higher School Certificate} \hfill \textbf{2020-2022}
		\begin{itemize}
			\item Milestone College.
			\item Subject: Science.
			\item G.P.A: 4.79
		\end{itemize}
		\item \textbf{Bachelor of Computer Science and Engineering} \hfill \textbf{2023-2027}
		\begin{itemize}
			\item American International University- Bangladesh.
			\item Subject: Computer Science and Engineering.
		\end{itemize}
	\end{itemize} 
	
	%--------------------EXPERIENCE----------------
	\begin{large}
		\underline {\textbf{Experience}} 
	\end{large}
	
	\begin{itemize}
		\item \textbf{Campus Ordinator, Quest of Latent Talent} \hfill \textbf{2020-2021} \par
		Promote leadership to the young, inspire them and find the excellence of creativity among the members.\par
		Invite members to show their creative arts, illustration, photography or any other creative arts                  
		\item \textbf{Tuition, Self-Employed} \hfill \textbf{2022-2023}\par
		Teach my friend, junior all subjects and tried to motivate them and encouraged them to solve their own problem.
		\item \textbf{Dream To Destination, Group Work} \hfill \textbf{2023}\par
		Tourist project with various types of packages and tried to improve the efficiency of the software \par
		Improve the packages, reduce time complexity store employees and guest list in the Project
		
		
	\end{itemize} 
	
	%--------------------EXTRA CURRICULAR ACTIVITIES----------------
	\begin{large}
		\underline {\textbf{Extra Curricular Activities}} 
	\end{large}
	
	\begin{itemize}
		\item \textbf{Member,LEO Club} \hfill \textbf{2021-2023}
		\begin{itemize}
			\item Donated money, food to the orphan , old age home
		\end{itemize}
		\item \textbf{Green Field School} \hfill \textbf{2015-2017}
		\begin{itemize}
			\item Music Club
			\item Art Club
		\end{itemize}
		\item \textbf{Scholars' School and College} \hfill \textbf{2019}
		\begin{itemize}
			\item Participate Math Quiz Competition
		\end{itemize}
		\item \textbf{United International University} \hfill \textbf{2024}
		\begin{itemize}
			\item Charity Fundraising for Flood Affected People
		\end{itemize}
	\end{itemize}
	
	%--------------------SKILLS----------------
	\begin{large}
		\underline {\textbf{Skills}} 
	\end{large}
	
	\begin{itemize}
		\item Certified in HTML, CSS, Bootstrap Web Development
		\item Skilled in MS Word, MS Powerpoint Figma, Autocad.
		\item Skilled in Google Docs.
		\item Leadership
		\item Skilled in LaTeX
		\item Self-Motivating
		\item Problem-Solving
		\item Time Management
	\end{itemize}
	
	%--------------------AWARDS----------------
	\begin{large}
		\underline {\textbf{Award}} 
	\end{large}
	
	\begin{itemize}
		\item Photography Award from American International University of Bangladesh \hfill \textbf{2022}
		\item Photography Award from Dhaka Shilpakala Academy \hfill \textbf{2022}
		
	\end{itemize}
	
	%--------------------HOBBY----------------
	\begin{large}
		\underline {\textbf{Hobby}} 
	\end{large}
	
	\begin{itemize}
		\item Photography
		\item Traveling
		\item Hiking
		
	\end{itemize}
	
	
\end{document}